\def\dMon{Mon, 03/15}
\def\dTues{Tues, 03/16}
\def\dWed{Wed, 03/17}
\def\dThur{Thur, 03/18}
\def\dFri{Fri, 03/19}
\def\dSat{Sat, 03/20}
\def\dSun{Sun, 03/21}
\placeDate

\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \itemHead{Workshops:} VFX in Blender (continued),Mixed Collages in 3D Space, Render Layers, Compositing, Video Editing, Motion Tracking
    \item \itemHead{Readings}[][Due on \dTues]
          \begin{itemize}
              \item \href{https://www.nytimes.com/2019/12/02/opinion/future-virtual-reality-stories.html}{\emph{It’s 2039, and Your Beloved Books Are Dead}}, Alix E. Harrow
              \item \textbf{Think about\dots} What is the ultimate form of narrative immersion? How do formats shape, describe, and prescribe the reality of their stories? Do these prescribed realities, like those in video games and movies, form a homogenous understanding of reality in contrast to books that leave the reader in charge of interpreting and imagining their reality? Submit your response to \discordR.
          \end{itemize}
    \item \itemHead{Exercise}[Project 2 Milestone][Due \dSun] Submit your preliminary progress towards the creation of Project 2. This can be integrating the creatures in the same scene, designing/modifying the habitats of the creatures, improving the lighting, materials, or the animation of your creatures, or additionally animation of elements in the environment. Submit the appropriate documentation (video or stills) to \discordE
    \item \itemHead{Exercise}[``Live Action'' Creature][Due \dSun] Place you creature in the motion tracked environment that we built during the workshops. Add additional elements to enhance, disrupt, or augment the existing environment from the video. Upload your video to Youtube or Vimeo and post the link to \discordE
    \item \itemHead{Challenge}[Cool Shadows][Due \dSun] Add realistic shadows to the exercise above. You can use Cycles a single shadow pass from Cycles, or use the complicated approach in EEVEE. If you do indeed complete this challenge, do not to resubmit the video, but simply post a still image that clearly shows your casted shadows to \discordC
    \item \itemHead{Screenings/Artists} Claudia Hart, Sophie Kahn, Marjan Moghaddam, Alfredo Salazar-Caro, Frederik Heyman, Cécile B. Evans
    \item \itemHead{Resources:}
          \begin{resenv}
              \begin{itemize}
                  \item \href{https://anthology.rhizome.org/}{Rhizome Anthology}
                  \item \href{https://www.e-flux.com/journal/}{e-flux}
                  \item \href{https://www.newmediaart.eu/}{NEWMEDIAART.EU}
              \end{itemize}
          \end{resenv}
\end{itemize}