\def\dMon{Mon, 01/11}
\def\dTues{Tues, 01/12}
\def\dWed{Wed, 01/13}
\def\dThur{Thur, 01/14}
\def\dFri{Fri, 01/15}
\def\dSat{Sat, 01/16}
\def\dSun{Sun, 01/17}
\placeDate

\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
      \item Introduction \& Discussion
      \item Claim Forms, Computer \& Door Access
      \item Syllabus Overview
      \item Logistics \& Communication
      \item Workshop
\end{itemize}
\vspace{1em}
% % \hrule
% \vspace{.5em}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
      \item \itemHead{Logistics}[][Responses Due \dThur]
            \begin{itemize}
                  \item Complete \href{https://forms.gle/MnFLmcqK7PUiKwra7}{Class Survey}
                  \item Fill Out \href{https://drive.google.com/file/d/1SeksTmFmQa6uehrmoSIL_uO8tuORo0P3/view}{Claims Form}
                        \newline Upload the completed form \href{https://osu.app.box.com/f/eb897914f2e94a08aace11a93668c046}{here} as \texttt{Lastname-Firstname.pdf}
            \end{itemize}
            \item \itemHead{Presentation}[Introduction][In-class \dThur] \newline Create a 5 minutes long presentation about yourself. This should include your previous works, expertise, and how/where you want to move forward in your career and practice. If you don't feel comfortable sharing your projects, instead include up to 3 works that interest you conceptually, technically, and aesthetically. Your presentations must be made with \href{https://docs.google.com/presentation/}{Google Slides}. Make sure it is shared with public access rights and share this public link in our Discord server under \discord{Exercises}{presentations}
      \item \itemHead{Challenge}[Blender Fundamentals][Due \dSun]
            \newline Your first challenge is aimed at familiarizing yourself with the software and putting into practice some of the techniques and skills that you learn along the way. For this challenge you are to watch \href{https://www.youtube.com/playlist?list=PLa1F2ddGya_-UvuAqHAksYnB0qL9yWDO6}{Blender Fundamentals}. Try to watch as many of these videos as you can. They serve as a perfect entry point to understand the Blender's capabilities. After you are done watching these videos, create a 10 seconds piece of animation at 24fps. Your animation requires keyframing the \ul{translation}, \ul{rotation}, and \ul{scale} of a primitive object (e.g. a cube or sphere). Anything beyond this is optional, but it would be nice to see your object shiny and nice looking \emoji{🤯💥👌}. Render your video as a 1080p .mp4 file and submit to our Discord server under \discordC
\end{itemize}