\def\dMon{Mon, 03/01}
\def\dTues{Tues, 03/02}
\def\dWed{Wed, 03/03}
\def\dThur{Thur, 03/04}
\def\dFri{Fri, 03/05}
\def\dSat{Sat, 03/06}
\def\dSun{Sun, 03/07}
\placeDate



% 
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \textbf{\textsc{Exercise 5} - Project 2 / Phase 2 (Due \dMon)} For this exercise, you are to show progress made towards your Project 2. This exercise is not meant to show ``\emph{how much}'' progress you have made, but to demonstrate that you are actively working towards your project 2. Submit proof of your prototypes, tests, kitbashing, lighting, camera work, \textbf{sound}, etc. These \textbf{must be submitted as a \href{https://docs.blender.org/manual/en/latest/editors/3dview/viewport_render.html}{viewport render} video that includes the sound}. Post your videos to the appropriate Discord channel.
    \item \textbf{\textsc{Exercise 6} - Project 2 / Phase 3 (Due \dSun)} For this exercise, you are to show progress made towards your Project 2. This exercise is not meant to show ``\emph{how much}'' progress you have made, but to demonstrate that you are actively working towards your project 2. Submit proof of your prototypes, tests, kitbashing, lighting, camera work, \textbf{sound}, etc. These \textbf{must be submitted as a \href{https://docs.blender.org/manual/en/latest/editors/3dview/viewport_render.html}{viewport render} video that includes the sound}. Post your videos to the appropriate Discord channel.
    \item \textcolor{defaultColor}{\textbf{Open Studio Week:}}
    \begin{itemize}
              \item Signup sheets are posted to Discord for Tuesday and Thursday. Feedback and hands-on problem-solving sessions will be provided during the entire class. Students are free to join either in person or virtually through Zoom. When you are signing up, select \textbf{ONE} of the available two days so that we can accommodate the campus safe and health policies.  Have your projects ready on an external disk to be brought to class.
              \item \textbf{Signup Sheet:} \href{https://docs.google.com/spreadsheets/d/1ipdRdrNSbPkMpchORybS6Fx0hvsXnFQzyQ64Ml3oH3A/edit?usp=sharing}{4401 Open Studios Signup Sheet}
          \end{itemize}
\end{itemize}