\def\dMon{Mon, 01/18}
\def\dTues{Tues, 01/19}
\def\dWed{Wed, 01/20}
\def\dThur{Thur, 01/21}
\def\dFri{Fri, 01/22}
\def\dSat{Sat, 01/23}
\def\dSun{Sun, 01/24}
\placeDate





% 
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \textbf{Individual Presentations (In-class \dMon)} Create a 5 minutes long presentation about yourself. This should include your previous works, expertise, and how/where you want to move forward in your career and practice. If you don't feel comfortable sharing your projects, instead include up to 3 works that interest you conceptually, technically, and aesthetically. Your presentations must be made with \href{https://docs.google.com/presentation/}{Google Slides}. Make sure they are publicly avaiable and share the public link in our Discord server: \textbf{Exercises $\Rightarrow$ \#presentations}
\end{itemize}
\vspace{1em}
\begin{itemize}[noitemsep,topsep=0pt,leftmargin=*]
    \item \textbf{Lessons:} Software, Motion, Movement in Digital Software, Keyframes, Attributes
    \item \textbf{\textsc{Exercise 1} - Blender Fundamentals (Due \dThur)} Your first exercise is aimed at solidifying and putting into practice some of the techniques and skills that you've learned while familiarizing yourself with \href{https://www.youtube.com/playlist?list=PLa1F2ddGya_-UvuAqHAksYnB0qL9yWDO6}{Blender Fundamentals}. Videos that apply to this exercise are 1, 2, 3, 4, 5, 6, 10, 21, 23, 24, 25, 38, 39, and 40 from the above Youtube playlist. For this exercise create a 10 seconds piece of animation at 24fps. Your animation requires keyframing the translation, rotation, and scaling of a primitive object (e.g. a cube). Anything beyond the requirement is optional. Render your video as a 1080p .mp4 file and submit to our Discord server.
    \item \textbf{Resources:} \href{https://sketchfab.com/search?features\=downloadable\&q\=scan+heritage\&sort\_by\=-relevance\&type\=models}{Sketchfab: 3D Foraging}
\end{itemize}